Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-03-27 apj.tex
committing everything that changed for the request for comments

As a check of the above interpretation, we generate a simulated dataset with the same numbers and uncertainties as our data, based on a
SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample, and $R^F$ values drawn from a log-normal
distribution with a mean of $2.4$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
measurement uncertainty are the only sources of variation in magnitudes.  As with the analysis of our data, we find that the
$\gamma$'s and \citetalias{1999PASP..111...63F}  vectors for nearly parallel planes, with the $\gamma^0$ vector consistent with
$\kappa_1=1/2.3$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.95in]{output11_sim/plane0.pdf}
   \includegraphics[width=2.95in]{output11_sim/plane1.pdf}
   \caption{
   Two perspectives of $UVI$- spaces
of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines), for a simulated dataset with
   input $R^F$ drawn from a log-normal distribution  with a mean of $2.4$ and 0.05 standard deviation.
   The combinations $a(X)+b(X)/2.3$ and  $a(X)+b(X)/2.4$ are shown in the dotted
   lines, the former is 
   almost  perfectly  superimposed on  $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
   \label{plane_sim:fig}}
\end{figure}

>>>>

As a check of the above interpretation, we generate a simulated dataset with the same numbers and uncertainties as our data, based on a
SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample, and $R^F$ values drawn from a log-normal
distribution with a mean of $\ln{2.4}$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
measurement uncertainty are the only sources of variation in magnitudes.  As with the analysis of our data, we find that the
$\gamma$'s and \citetalias{1999PASP..111...63F}  vectors for nearly parallel planes, with the $\gamma^0$ vector almost consistent with
$\kappa_1^{-1}=2.4$, as expected given the mean of $\ln{2.4}$ of the input log-normal distribution.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.95in]{output11_sim/plane0.pdf}
   \includegraphics[width=2.95in]{output11_sim/plane1.pdf}
   \caption{
   Two perspectives of $UVI$- spaces
of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines), for a simulated dataset with
   input $R^F$ drawn from a log-normal distribution  with a mean of $\ln{2.4}$ and 0.05 standard deviation.
   The combinations $a(X)+b(X)/2.3$ and  $a(X)+b(X)/2.4$ are shown in the dotted
   lines, the former is 
   almost  perfectly  superimposed on  $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
   \label{plane_sim:fig}}
\end{figure}
